### 2020-05-31 writeup/transfer.tex
sec 2
sec 3 wip

\section{Understanding Negative Transfer and Their Algorithmic Implications}\label{sec_insight}

Based on the key lemma, we explain three contributing factors of negative transfer, including task dissimilarity, large source data size and covariate shift.
For each factor, we show how negative transfer occurs using a simplified isotropic model.
Then, we describe the algorithmic implication of the theory.

\subsection{Task Similarity}\label{sec_similarity}

>>>>

\section{Explaining the Phenomena of Negative Transfer in Multi-Task Learning}\label{sec_insight}

Based on the key lemma, we provide rigorous explanations to the phenomena of negative transfer in multi-task learning.
We study three components, including task model, data size and covariate shift.
For each component, we show how negative transfer occurs using a simplified isotropic model.
Then, we describe the algorithmic consequence of the theory.

\subsection{Task Model}\label{sec_similarity}
